---
title: "Figures"
author: "Maddy Kline"
date: "2023-06-06"
output:
  pdf_document: default
  html_document: default
---

```{r global options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
library(ggplot2)
library(usmap)
library(gridExtra)
library(maps)
library(mapdata)
library(ggmap)
library(lmtest)
library(tidycensus)
library(data.table)
library(RColorBrewer)
library(rgdal)
library(broom)
library(ggpattern)
library(ggrepel)
library(USpopcenters)
library(gifski)
library(animation)

set.seed(2023)
```


# Read in data
```{r read_data}
dat <- read_csv("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/old/fulldat.csv") #change this path to be accurate
coh <- read_csv("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/old/GeoCohort.csv") #change path to be accurate

#set color palette for regions
colors_df <- data.frame(Region = c("South", "Midwest", "Northeast", "West"),
                        region_color = c("#DE6C83", "#43AA8B", "#2274A5", "#EDDEA4"))

#set color palette for subregions (subdivisions of regions)
pal <- brewer.pal(n= 9, name = "Paired")
subcolors_df <- data.frame(Region = c("East South Central", "West South Central",
                                      "West North Central", "South Atlantic", "Middle Atlantic",
                                      "Mountain West", "East North Central", "New England", "Pacific West"),
                           region_color = c(pal[6], pal[5], pal[4], pal[9], pal[2], pal[8], pal[3], pal[1], pal[7]))


```
# Read in helper files
```{r}
source("get_popsizes.R")
source("get_regions.R")
source("get_subregions.R")
source("yearly_average_functions.R")
source("monthly_average_functions.R")
source("get_state_sinusoids.R")
source("region_subregion_sinusoid_functions.R")
```




Calculate the proportion of the population represented in the dataset for calculation in line 110
```{r pop proportion}
total_us_pop_years_df <- data.frame(YEAR = c(2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018), 
                                    pop = c(309414110, 311580009, 313874218, 316057727, 318386421,
                                            320742673, 323071342, 325147121, 327167434))
yearly_memb <- coh |> group_by(YEAR) |>
  summarize(yearly_memb = sum(NMEMB))
#percentage of population represented by the database
rep <- left_join(yearly_memb, total_us_pop_years_df) |> mutate(perc = yearly_memb / pop)
rep |> arrange(yearly_memb)
```



# Summarize characteristics of the cohort
Average membership by sex, age group, region, and subregion. Becomes Table 1.
```{r table1}
#total
total_range <- coh |> group_by(YEAR) |>
  summarize(membership = sum(NMEMB)) |>
  summarize(avg_membership = mean(membership), min = min(membership), max = max(membership))

total_df <- data.frame(Category = "Total", avg_membership = total_range$avg_membership, 
                       perc = 1, min = total_range$min, max = total_range$max)

total_avg_memb <- total_df$avg_membership

#sex membership
sex_membership <- coh |> group_by(SEX, YEAR) |>
  summarize(membership = sum(NMEMB)) |>
  group_by(SEX) |>
  summarize(avg_membership = mean(membership), min = min(membership), max = max(membership)) |>
  mutate(perc = avg_membership / total_avg_memb) |>
  mutate(Category = SEX) |>
  mutate(Category = c("Male", "Female")) |>
  select(Category, avg_membership, perc, min,max) 

#age membership
age_membership <- coh |> group_by(AGEGRP, YEAR) |>
  summarize(membership = sum(NMEMB)) |>
  group_by(AGEGRP) |>
  summarize(avg_membership = mean(membership), min = min(membership), max = max(membership)) |>
  mutate(perc = avg_membership / total_avg_memb) |>
  mutate(Category = AGEGRP) |>
  select(Category, avg_membership, perc, min, max) 


#region membership
regions_membership <- coh |> 
  left_join(regions) |> group_by(part, YEAR) |>
  summarize(membership = sum(NMEMB)) |>
  group_by(part) |>
  summarize(avg_membership = mean(membership), min = min(membership), max = max(membership)) |> mutate(Category = str_to_title(part)) |>
  select(Category, avg_membership, min, max) |> 
  mutate(perc = avg_membership / total_avg_memb) |>
  select(Category, avg_membership, perc, min, max)

#subregion membership
subregions_membership <- coh |> left_join(subregions) |> group_by(part, YEAR) |>
  summarize(membership = sum(NMEMB)) |>
  group_by(part) |>
  summarize(avg_membership = mean(membership), min = min(membership), max = max(membership))

subregions_membership <- subregions_membership |> mutate(Category = gsub("_", " ", subregions_membership$part, fixed=TRUE)) |>
  select(Category, avg_membership, min, max) |> 
  mutate(perc = avg_membership / total_avg_memb) |>
  select(Category, avg_membership, perc, min, max)

sex_df <- data.frame(Category = "Sex", avg_membership = NA, 
                     perc = NA, min = NA, max = NA)

age_df <- data.frame(Category = "Age Group", avg_membership = NA, 
                     perc = NA, min = NA, max = NA)
subregion_df <- data.frame(Category = "Subregion", avg_membership = NA, 
                        perc = NA, min = NA, max = NA)
region_df <- data.frame(Category = "Region", avg_membership = NA, 
                        perc = NA, min = NA, max = NA)

table1 <- rbind(total_df, sex_df, sex_membership, age_df, age_membership, region_df, regions_membership, subregion_df, subregions_membership)|>
  mutate(Average_Membership = format(avg_membership, scientific = TRUE, digits = 3),
         min = format(min, scientific = TRUE, digits = 3),
         max = format(max, scientific = TRUE, digits = 3)) |>
  mutate("%" = round(perc*100, 2),
        Average_Membership = paste0(Average_Membership," ","(", min, "-", max, ")")) |>
  select(Category, Average_Membership, `%`)

```

# Calculate average membership by state
For quality control, threshold was set at an average of >5,000 members per year. Becomes Supplementary Figure 1.
```{r figS1}
continental_state_membership_noSC <- coh |> 
  filter(!STATE %in% c('Hawaii', 'Alaska', 'South Carolina')) |> 
  group_by(STATE, YEAR) |> 
  summarize(total_memb = sum(NMEMB)) |>
  group_by(STATE) |>
  summarize(NMEMB = mean(total_memb)) |>
  ggplot(aes(x = reorder(STATE, -NMEMB), y = log(NMEMB))) + 
  geom_bar(stat = "identity") +
  geom_hline(yintercept = log(5000), linetype = 2, color = "red") +
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  # ggtitle("Average Yearly Membership by State, 2010-2018") +
  ylab("Log Average Yearly Membership") +
  xlab("State")

```


# Yearly regional and subregional differences in disease burden
Calculate the total visits per 1000 members across all years by region. Becomes figure S2a.
```{r Figure S2a}
vis_year <- dat |> group_by(STATE, SEX, AGEGRP, YEAR) |> summarize(yearly_visits = sum(NVISITS))
regions_weighted_allyears <- get_yearly_differences(regions) |> mutate(Region = str_to_title(part)) |> 
  left_join(colors_df) |> mutate(Region = factor(Region, levels = c("South", "Midwest", "Northeast", "West")))
#plot 
region_differences_byyear <- regions_weighted_allyears |> ggplot(aes(YEAR, sum_region_cases_per_thousand, group = Region, color=Region)) +
  geom_line() + scale_color_manual(values= colors_df$region_color) + theme_minimal() +
  ylab("Visits per 1000") + xlab("Year") + labs(color = "Region") + 
  # ggtitle("Streptococcal Pharyngitis Visits by Region over Time") +
  theme(plot.title = element_text(hjust = 0.5, size = 20))

region_differences_byyear_forfig <- regions_weighted_allyears |> ggplot(aes(YEAR, sum_region_cases_per_thousand, group = Region, color=Region)) +
  geom_line() + scale_color_manual(values= colors_df$region_color) + theme_minimal() +
  ylab("Visits per 1000") + xlab("Year") + labs(color = "Region") + 
  # ggtitle("Streptococcal Pharyngitis Visits by Region over Time") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), legend.position = "none")
```

Calculate average visits per year in each region and statistically compare
```{r supplementary Figure 2}
avg_yearly_regions <- regions_weighted_allyears |>
  group_by(Region) |>
  summarize(avg_vis_thous = mean(sum_region_cases_per_thousand), sd = sd(sum_region_cases_per_thousand)) |>
  mutate(lower = avg_vis_thous - 1.96*sd/sqrt(9), upper = avg_vis_thous + 1.96*sd/sqrt(9)) |>
  mutate(Region = factor(Region, levels = c("South", "Midwest", "Northeast", "West"))) |>
  arrange(Region)

region_table <- avg_yearly_regions |>
  mutate("95%CI" = paste0("(", round(lower,2), "-", round(upper,2), ")")) |>
  select(Region, avg_vis_thous, `95%CI`)

year_averages_plot <- avg_yearly_regions |> 
  ggplot(aes(Region, avg_vis_thous, color = Region)) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  scale_color_manual(values= colors_df$region_color, labels = colors_df$Region) +
  ylab("Visits per 1000") +
  # ggtitle("Streptococcal Pharyngitis Average Visits by Region") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 20))


#make dataframe and perform each t-test
ttest_table_reg <- expand_grid(region1 = c("South", "Midwest", "Northeast", "West"), 
            region2 = c("South", "Midwest", "Northeast", "West")) |>
  filter(region1 != region2) |>
  mutate(Comparison = paste0(region1, "-", region2)) |>
  filter(!Comparison %in% c("Midwest-South", "Northeast-South", "Northeast-Midwest",
                            "West-South", "West-Midwest", "West-Northeast"))

ttest_table_reg <- fill_table(ttest_table_reg, regions_weighted_allyears, avg_yearly_regions)

region_comparisons <- ttest_table_reg |> 
  ggplot(aes(x = -log(pvals), y = diff, shape = Comparison)) +
  geom_point() +
  geom_vline(xintercept = -log(0.05/6), linetype = 2, color = "red") +
  xlab("Negative Log P-value") +
  ylab("Difference in Visits per 1000") + 
  # ggtitle("Streptococcal Pharyngitis Average Yearly Region Comparisons") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18))
```

Total visits per 1000 members across all years by subregion as well as calculation of average visits per year in each region and statistical comparison. Becomes Supplementary Figure 3.
```{r Supplementary Figure 3}
subregions_weighted_allyears <- get_yearly_differences(subregions) |> mutate(Region = str_to_title(part)) |> 
  left_join(subcolors_df) |> mutate(Region = factor(Region, levels = subcolors_df$Region))

subregion_differences_byyear <- subregions_weighted_allyears |> ggplot(aes(YEAR, sum_region_cases_per_thousand, group = Region, color=Region)) +
  geom_line() + scale_color_manual(values= subcolors_df$region_color) + theme_minimal() +
  ylab("Visits per 1000") + xlab("Year") + labs(color = "Subegion") + 
  # ggtitle("Streptococcal Pharyngitis Visits by Subregion over Time") +
  theme(plot.title = element_text(hjust = 0.5, size = 20))

subregion_differences_byyear_forfig <- subregions_weighted_allyears |> ggplot(aes(YEAR, sum_region_cases_per_thousand, group = Region, color=Region)) +
  geom_line() + scale_color_manual(values= subcolors_df$region_color) + theme_minimal() +
  ylab("Visits per 1000") + xlab("Year") + labs(color = "Subegion") + 
  # ggtitle("Streptococcal Pharyngitis Visits by Subregion over Time") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), legend.position = "none")

avg_yearly_subregions <- subregions_weighted_allyears |>
  group_by(Region) |>
  summarize(avg_vis_thous = mean(sum_region_cases_per_thousand), sd = sd(sum_region_cases_per_thousand)) |>
  mutate(lower = avg_vis_thous - 1.96*sd/3, upper = avg_vis_thous + 1.96*sd/3) |>
  arrange(-avg_vis_thous) |> 
  left_join(subcolors_df)
order <- avg_yearly_subregions |> pull(Region)  
avg_yearly_subregions <- avg_yearly_subregions |>
  mutate(Region = factor(Region, levels = order))

#write_csv(avg_yearly_subregions, "year_subregions_sd.csv")

subregion_table <- avg_yearly_subregions |>
  mutate("95%CI" = paste0("(", round(lower,2), "-", round(upper,2), ")")) |>
  select(Region, avg_vis_thous, `95%CI`)

year_averages_plot_subregions <- avg_yearly_subregions |> 
  ggplot(aes(reorder(Region, -avg_vis_thous), avg_vis_thous, color = Region)) + 
  geom_point() +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  scale_color_manual(values= avg_yearly_subregions$region_color, labels = avg_yearly_subregions$Region) +
  ylab("Visits per 1000") + 
  # ggtitle("Streptococcal Pharyngitis Average Visits by Region") +
  theme_minimal() +
  xlab("Region") + 
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=0.5),
        plot.title = element_text(hjust = 0.5, size = 20)) 

ttest_table_sub <- expand_grid(region1 = subregion_table$Region, 
                           region2 = subregion_table$Region) |>
  filter(region1 != region2) |>
  mutate(Comparison = paste0(region1, "-", region2)) |>
  filter(!Comparison %in% c("West South Central-East South Central",
                            "West North Central-East South Central",
                            "West North Central-West South Central",
                            "South Atlantic-East South Central",
                            "South Atlantic-West South Central",
                            "South Atlantic-West North Central",
                            "Middle Atlantic-East South Central",
                            "Middle Atlantic-West South Central",
                            "Middle Atlantic-West North Central",
                            "Middle Atlantic-South Atlantic",
                            "Mountain West-East South Central",
                            "Mountain West-West South Central",
                            "Mountain West-West North Central",
                            "Mountain West-South Atlantic",
                            "Mountain West-Middle Atlantic",
                            "East North Central-East South Central",
                            "East North Central-West South Central",
                            "East North Central-West North Central",
                            "East North Central-South Atlantic",
                            "East North Central-Middle Atlantic",
                            "East North Central-Mountain West",
                            "New England-East South Central",
                            "New England-West South Central",
                            "New England-West North Central",
                            "New England-South Atlantic",
                            "New England-Middle Atlantic",
                            "New England-Mountain West",
                            "New England-East North Central",
                            "Pacific West-East South Central",
                            "Pacific West-West South Central",
                            "Pacific West-West North Central",
                            "Pacific West-South Atlantic",
                            "Pacific West-Middle Atlantic",
                            "Pacific West-Mountain West",
                            "Pacific West-East North Central",
                            "Pacific West-New England"
                            
                            ))

ttest_table_sub <- fill_table(ttest_table_sub, subregions_weighted_allyears,avg_yearly_subregions)
subregion_comparisons <- ttest_table_sub |> 
  ggplot(aes(x = -log(pvals), y = diff, color = Comparison)) +
  geom_point() + geom_text_repel(aes(label = Comparison)) +
  geom_vline(xintercept = -log(0.05/36), linetype = 2, color = "red") +
  xlab("Negative Log P-value") +
  ylab("Difference in Visits per 1000") + 
  # ggtitle("Streptococcal Pharyngitis Average Yearly Subregion Comparisons") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none")
```

# Average monthly regional and subregional differences 
Calculate average monthly visits by region, becomes Figure 1.
```{r Figure 1}
regions_weighted_allyears <- calculate_averages(c("Hawaii", "Alaska"), regions)[[2]] |> 
  mutate(Region = str_to_title(part)) |> 
  left_join(colors_df) |> mutate(Region = factor(Region, levels = c("South", "Midwest", "Northeast", "West")))

regions_weighted <- calculate_averages(c("Hawaii", "Alaska"), regions)[[3]] |>
  mutate(Region = str_to_title(part)) |> 
  left_join(colors_df) |> mutate(Region = factor(Region, levels = c("South", "Midwest", "Northeast", "West")))
  

points_region_plot <- plot_averages_CIs_points(regions_weighted, 
                         regions_weighted_allyears,
                         colors_df) + labs(title = NULL) + xlab("Month")

#corresponding table of values
region_table_month <- calculate_averages(c("Hawaii", "Alaska"), regions)[[3]] |> 
  mutate(CI = paste0("(", round(yearly_average_sum_region_cases_per_thousand - 1.96*sd/3, 2), "-", 
                     round(yearly_average_sum_region_cases_per_thousand + 1.96*sd/3, 2), ")")) |>
  mutate(Region = str_to_title(part), 
         Month = MONTH,
         Visits_per_1000 = yearly_average_sum_region_cases_per_thousand) |>
  mutate('Visits(CI)' = paste(round(Visits_per_1000,2), CI)) |>
  select(Region, Month, `Visits(CI)`) 
  
region_table_month <- region_table_month[,2:4] |> pivot_wider(names_from = Region, values_from = `Visits(CI)`)

```

Average subregional differences over the course of the year. Becomes Supplementary Figure 4.
```{r supplementary figure 4}
subregions_weighted_allyears <- calculate_averages(c("Hawaii", "Alaska"), subregions)[[2]] |> 
  mutate(Region = factor(str_to_title(part), levels = c("East South Central", "West South Central",
                                      "West North Central", "South Atlantic", "Middle Atlantic",
                                      "Mountain West", "East North Central", "New England", "Pacific West"))) 

subregions_weighted <- calculate_averages(c("Hawaii", "Alaska"), subregions)[[3]] |>
  mutate(Region = factor(str_to_title(part), levels = c("East South Central", "West South Central",
                                      "West North Central", "South Atlantic", "Middle Atlantic",
                                      "Mountain West", "East North Central", "New England", "Pacific West")))
  

points_subregion_plot <- plot_averages_CIs_points(subregions_weighted, 
                         subregions_weighted_allyears,
                         subcolors_df) + labs(title = NULL) + xlab("Month")

#tables with corresponding values
subregion_table_month <- calculate_averages(c("Hawaii", "Alaska"), subregions)[[3]] |> 
  mutate(CI = paste0("(", round(yearly_average_sum_region_cases_per_thousand - 1.96*sd/3, 2), "-", 
                     round(yearly_average_sum_region_cases_per_thousand + 1.96*sd/3, 2), ")")) |>
  mutate(Region = str_to_title(part), 
         Month = MONTH,
         Visits_per_1000 = yearly_average_sum_region_cases_per_thousand) |>
  mutate('Visits(CI)' = paste(round(Visits_per_1000,2), CI)) |>
  select(Region, Month, `Visits(CI)`) 

subregion_table_month <- subregion_table_month[,2:4] |> 
  mutate(Region = gsub("_", " ",subregion_table_month$Region , fixed=TRUE)) |>
  mutate(Region = str_to_title(Region)) |>
  pivot_wider(names_from = Region, values_from = `Visits(CI)`)
```


# Average quarterly visits between regions and subregions
Calculate average quarterly visits over 3 month chunks, becomes Figure S5a
```{r supplementary figure 5a}
quarter_df <- data.frame(MONTH = c(1:12), quarter = c(1,1,1,2,2,2,3,3,3, 4,4,4))
quarters <- left_join(regions_weighted_allyears, quarter_df) |> group_by(part, YEAR, quarter) |> summarize(quarter_vis = sum(sum_region_cases_per_thousand)) |>
  mutate(part = factor(part, levels = c("South", "Midwest", "Northeast", "West")))


region_quarters_plot <- quarters |> group_by(part, quarter) |> summarize(avg_quart_vis = mean(quarter_vis), sd= sd(quarter_vis)) |>
  mutate(lower = avg_quart_vis - 1.96*sd/3, upper = avg_quart_vis + 1.96*sd/3) |>
  ggplot(aes(quarter, avg_quart_vis, fill = part)) + geom_bar(position = 'dodge', stat = 'identity') +
  geom_errorbar(aes(x =quarter, ymin = lower, ymax = upper), position = 'dodge',  alpha = 0.2)+ scale_fill_manual(values = colors_df$region_color, labels = colors_df$Region) + theme_minimal() + labs(fill = "Region") + ylab("Visits per 1000 People") + xlab("Quarter")

#save table of average quarterly values
region_quarters_table <- quarters |> group_by(part, quarter) |> summarize(avg_quart_vis = mean(quarter_vis), sd= sd(quarter_vis)) |>
  mutate(lower = avg_quart_vis - 1.96*sd/3, upper = avg_quart_vis + 1.96*sd/3) |>
  mutate("Average_Visits(95%CI)" = paste0(round(avg_quart_vis, 2), " ", "(", round(lower,2), "-", round(upper, 2), ")")) |>
  select(part, quarter, `Average_Visits(95%CI)`)

```

Calculate average subregional visits over 3 month chunks, becomes Figure S5b
```{r supplementary figure 5b}
sub_quarters <- left_join(subregions_weighted_allyears, quarter_df) |> group_by(part, YEAR, quarter) |> summarize(quarter_vis = sum(sum_region_cases_per_thousand)) |> mutate(part = factor(part, levels = c("East South Central", "West South Central",
                                      "West North Central", "South Atlantic", "Middle Atlantic",
                                      "Mountain West", "East North Central", "New England", "Pacific West")))

subregion_quarters_plot <- sub_quarters |> group_by(part, quarter) |> summarize(avg_quart_vis = mean(quarter_vis), sd= sd(quarter_vis)) |>
  mutate(lower = avg_quart_vis - 1.96*sd/3, upper = avg_quart_vis + 1.96*sd/3) |>
  ggplot(aes(quarter, avg_quart_vis, fill = part)) + geom_bar(position = 'dodge', stat = 'identity') +
  geom_errorbar(aes(x =quarter, ymin = lower, ymax = upper), position = 'dodge',  alpha = 0.2)+ scale_fill_manual(values = subcolors_df$region_color, labels = subcolors_df$Region) + theme_minimal() + labs(fill = "Subregion") + ylab("Visits per 1000 People") + xlab("Quarter")

subregion_quarters_table <- sub_quarters |> group_by(part, quarter) |> summarize(avg_quart_vis = mean(quarter_vis), sd= sd(quarter_vis)) |>
  mutate(lower = avg_quart_vis - 1.96*sd/3, upper = avg_quart_vis + 1.96*sd/3) |>
  mutate("Average_Visits(95%CI)" = paste0(round(avg_quart_vis, 2), " ", "(", round(lower,2), "-", round(upper, 2), ")")) |>
  select(part, quarter, `Average_Visits(95%CI)`)

```

Calculate average differences between regions, becomes Supplementary Table 4 
```{r table S4}
#initialize df
quarter_diff_allyears <- expand_grid(Comparison = c("West-South", "West-Northeast", "West-Midwest", "South-Northeast", "South-Midwest", "Northeast-Midwest"), Year = c(2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018), Quarter = c(1,2,3,4)) |> mutate(Diff = NA)

#loop through rows in df and fill 
for(i in 1:nrow(quarter_diff_allyears)){
  R1 = quarters |> filter(part == strsplit(quarter_diff_allyears$Comparison[i], "-")[[1]][1], 
                          YEAR == quarter_diff_allyears$Year[i],
                          quarter == quarter_diff_allyears$Quarter[i]) |>
    pull(quarter_vis)
  R2 = quarters |> filter(part == strsplit(quarter_diff_allyears$Comparison[i], "-")[[1]][2], 
                          YEAR == quarter_diff_allyears$Year[i],
                          quarter == quarter_diff_allyears$Quarter[i]) |>
    pull(quarter_vis)
  quarter_diff_allyears$Diff[i] <- R1-R2
}

quarter_diffs_table <- quarter_diff_allyears |> group_by(Comparison, Quarter) |> summarize(avg_diff = mean(as.numeric(Diff)), sd = sd(as.numeric(Diff))) |> 
  mutate(abs_avg_diff = abs(avg_diff), 
         lower = abs_avg_diff - 1.96*sd/3,
         upper = abs_avg_diff + 1.96*sd/3) |>
  mutate('Abs_Avg_diff(CI)' = paste0(round(abs_avg_diff, 2), " ", "(", round(lower, 2), "-", round(upper, 2), ")")) |>
  select(Comparison, Quarter, `Abs_Avg_diff(CI)`)

```

# Statistically compare each month and region or subregion
T-tests comparing each region-month, becomes Supplementary Figure 6a 
```{r supplementary figure 6a}
#create table of regional differences and p-values from T-test
#using helper function "get_diff_df" from "monthly_average_functions.R"
wide_table_regions <- get_diff_df(c("Hawaii", "Alaska"), regions) |>
  filter(region1 != region2) |> 
  mutate("Diff(pval)" = paste0(round(diff,3), "(",round(pval,8), ')')) |>
  select(-region1, -region2, -diff, -pval) |>
  pivot_wider(names_from = Comparison, values_from = `Diff(pval)`)

#build heat map
#calculate regional differences
region_US_cont <- get_diff_df(c("Hawaii", "Alaska"), regions) 

#calculate bonferroni-corrected p-value threshold
val <- 0.05 / nrow(region_US_cont)

#remove self and redundant comparisons
region_heatmap_significance_noredund <- region_US_cont |> mutate(sig = ifelse(pval < val, 0,1)) |> 
  filter(region1 != region2) |> 
  filter(!Comparison %in% c("South-West", "Northeast-West", 
                            "Northeast-South", "Midwest-West", 
                            "Midwest-Northeast", "Midwest-South")) |>
  ggplot(aes(x = MONTH, y = Comparison, fill = factor(sig))) + geom_tile() + 
  xlab("Month") +
  scale_fill_manual(values = c('#0096FF','grey'),  labels = c("Yes", "No")) + theme_minimal() + 
  labs(fill = "Significant") +
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size = 20)) 

```

T-tests comparing each subregion-month, becomes Supplementary Figure 6b
```{r supplementary figure 6b}
#create table of subregional differences and p-values from T-test
wide_table_subregions <- get_diff_df(c("Hawaii", "Alaska"), subregions) |> 
  filter(region1 != region2) |> 
  mutate("Diff(pval)" = paste0(round(diff,3), "(",round(pval,8), ')')) |>
  select(-region1, -region2, -diff, -pval) |>
  pivot_wider(names_from = Comparison, values_from = `Diff(pval)`)

#subregion heat map 
subregion_order_heatmap <- data.frame(region2 = c("Pacific West", "Mountain West", "West North Central", "West South Central","East North Central", "East South Central", "Middle Atlantic","South Atlantic", "New England"),order = c(1:9))
subregion_US_cont <- get_diff_df(c("Hawaii", "Alaska"), subregions) 
val2 <- 0.05 / nrow(subregion_US_cont)
subregion_US_cont <- subregion_US_cont |> 
  mutate(sig = ifelse(pval < val2, 0,1)) |> 
  filter(region1 != region2)

#remove redundancies
subregion_US_cont2 <- subregion_US_cont |>
  filter(!Comparison %in% c("Pacific West-Mountain West",
                            "Pacific West-West North Central",
                            "Mountain West-West North Central",
                            "Pacific West-West South Central",
                            "Mountain West-West South Central",
                            "West North Central-West South Central",
                            "Pacific West-East North Central",
                            "Mountain West-East North Central",
                            "West North Central-East North Central",
                            "West South Central-East North Central",
                            "Pacific West-East South Central",
                            "Mountain West-East South Central",
                            "West North Central-East South Central",
                            "West South Central-East South Central",
                            "East North Central-East South Central",
                            "Pacific West-Middle Atlantic",
                            "Mountain West-Middle Atlantic",
                            "West North Central-Middle Atlantic",
                            "West South Central-Middle Atlantic",
                            "East North Central-Middle Atlantic",
                            "East South Central-Middle Atlantic",
                            "Pacific West-South Atlantic",
                            "Mountain West-South Atlantic",
                            "West North Central-South Atlantic",
                            "West South Central-South Atlantic",
                            "East North Central-South Atlantic",
                            "East South Central-South Atlantic",
                            "Middle Atlantic-South Atlantic",
                            "Pacific West-New England",
                            "Mountain West-New England",
                            "West North Central-New England",
                            "West South Central-New England",
                            "East North Central-New England",
                            "East South Central-New England",
                            "Middle Atlantic-New England",
                            "South Atlantic-New England")) |>
  left_join(subregion_order_heatmap) |> 
  group_by(MONTH) |>
  arrange(order) |>
  mutate(Comparison2 = str_to_title(gsub("_", " ", Comparison, fixed=TRUE))) |>
  select(-Comparison) |>
  mutate(Comparison = Comparison2) |>
  select(-Comparison2)

subregion_heatmap_significance_noredund <- subregion_US_cont2 |> 
  ggplot(aes(x = MONTH, y = reorder(Comparison, -order), fill = factor(sig))) + geom_tile() + 
  scale_fill_manual(values = c('#0096FF','grey'),  labels = c("Yes", "No")) + theme_minimal() + 
  ylab("Comparison") + 
  xlab("Month") +
  labs(fill = "Significant") +
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size = 25))
```


# Sinusoidal Fitting
Fitting state visit trends to sinusoids
```{r state phases, supplementary table 5}
#state_sinusoids_parameters and state_sinusoids called from get_state_sinusoids.R helper file
#make a table of all state phases (Supplementary Table 5)
phase_table <- state_sinusoids_parameters |> mutate(Phase_corrected = Phase %% 12) |>
  mutate(Phase_lower = Phase_corrected - 1.96*Phase_SE,
         Phase_upper = Phase_corrected + 1.96*Phase_SE) |>
  mutate(Final_phase = paste0(round(Phase_corrected,2), " ", "(", round(Phase_lower,2), "-", round(Phase_upper,2), ")")) |>
  filter(!State %in% c("South Carolina", "Hawaii", "Alaska")) |>
  select(State, Final_phase) |>
  mutate("Phase(95% CI)" = Final_phase) |>
  select(-Final_phase)
```


Plot state phases on a map of the U.S., becomes Figure 2.
```{r figure 2}
#load US shapefile
my_spdf <- readOGR(dsn = "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/Strep_project/R code/plots/More_final_figures/mapping/cb_2018_us_state_500k",
                   layer = "cb_2018_us_state_500k")
# https://www.census.gov/geographies/mapping-files/time-series/geo/carto-boundary-file.html
spdf_fortified <- tidy(my_spdf)

#remove non-continental US states and territories
non_continental_ids <- which(!(my_spdf$NAME %in% c("American Samoa" , 
                                   "Commonwealth of the Northern Mariana Islands", 
                                   "Guam",
                                   "Hawaii",
                                   "Alaska",
                                   "Puerto Rico",
                                   "United States Virgin Islands")))
continental <- my_spdf[non_continental_ids,]

#fortify shapefile
continental_fortified <- tidy(continental)

#add back in state names which were lost in tidy()
temp_df <- data.frame(my_spdf@data$NAME)
names(temp_df) <- c("NAME")
temp_df$id <-as.character(seq(0, nrow(temp_df)-1))
state_names <- left_join(continental_fortified, temp_df) |> mutate(State = NAME) |> select(-NAME)
continental_fortified_tojoin <- left_join(continental_fortified, state_names) |> select(-id) |> mutate(id = State) |> select(-State)

#correct state phases for map
state_sinusoids_parameters_tojoin <- state_sinusoids_parameters |> mutate(Phase_corrected = Phase %% 12, 
                                                                          id = State) |> select(id, Phase_corrected)
#add phase data to shapefile
continental_phases <- left_join(continental_fortified_tojoin, state_sinusoids_parameters_tojoin) 
#remove South Carolina
continental_phases_noSC <- continental_phases
continental_phases_noSC[which(continental_phases_noSC$id == "South Carolina"),8] = NA
sc <- continental_phases[which(continental_phases$id == "South Carolina"),]
state_phases_map_noSC <- ggplot() + 
  geom_polygon(data = continental_phases_noSC, aes(x = long, y = lat, group = group, fill = Phase_corrected), color="black") +
  geom_polygon_pattern(data = sc, aes(x = long, y = lat, group= group), fill = "gray", pattern = 'stripe', 
                       pattern_spacing = 0.005, pattern_alpha = 0.5) +
  theme_void() + ggtitle("") + scale_fill_gradient(low = "#30239B", high =  "#FFFFFF", breaks = c(0, 1, 2, 3), 
                                                   labels = c("Dec", "Jan", "Feb", "Mar"),
                                                   limits = range(0,3)) + 
  labs(fill = "Peak Month") +
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        plot.subtitle = element_text(hjust = 0.5, size = 23),
        legend.position = 'bottom')
```
Plot state sinusoids with confidence intervals, becomes Supplementary Figure 10
```{r supplementary figure 9}
state_sinusoids_subregions <- ggplot() + 
  geom_point(aes(x = MONTH, y = mean_weighted_cases_per_thousand, color = Region), data = state_sinusoids_withCIs_cont_sub, size = 0.5) + 
  geom_ribbon(aes(x = MONTH, ymin = lower, ymax = upper, fill = Region), data = state_sinusoids_withCIs_cont_sub, alpha = 0.2) +
  geom_line(aes(x = MONTH, y = prediction, color = Region), data = state_sinusoids_withCIs_cont_sub, linetype = 2) +
  scale_color_manual(values= subcolors_df$region_color, labels=gsub("_", " ",subcolors_df$Region , fixed=TRUE)) +
  scale_fill_manual(values = subcolors_df$region_color, labels=gsub("_", " ",subcolors_df$Region , fixed=TRUE)) +
  facet_wrap(~STATE) +
  # ggtitle("Streptococcal Pharyngitis Visits State Sinusoidal Fits") +
  labs(color = "Subregion", fill = "Subregion") + 
  xlab("Month") +
  ylab("Visits per 1,000 People") +
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size = 20)) 
```

Fit sinusoids to region trends and plot. Becomes Supplementary Figure 9a. 
```{r regional sinusoids plot, supplementary figure 8a}
#get_regions_sinusoids() from "region_subregion_sinusoid_functions.R"
region_sinusoids <- get_region_sinusoids(c("Hawaii", "Alaska"))[[1]] |>
   mutate(Region = factor(part, levels = c("South", "Midwest", "Northeast", "West")))

region_sinusoids_CIs_plot_points <- region_sinusoids |>
  ggplot(aes(x=MONTH)) + 
  geom_line(aes(x= MONTH, y = prediction, color = Region), linetype = 2) + 
  geom_point(aes(x= MONTH, y = yearly_average_sum_region_cases_per_thousand, color = Region), size = 1, data = region_sinusoids) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill= Region), alpha = 0.2) +
  # ggtitle("Streptococcal Pharyngitis Visits Region Sinusoidal Fits") +
  xlab("Month") +
  labs(color = "Region", fill = "Region") + 
  ylab("Cases per 1,000 People") +
  scale_color_manual(values= colors_df$region_color, labels = colors_df$Region) +
  scale_fill_manual(values = colors_df$region_color, labels = colors_df$Region) +
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size = 20)) 

```

Plot regional sinusoid phases. Becomes Supplementary Figure 9b.
```{r plot reginoal sinusoid phases, supplementary figure 8b}
region_sinusoids_parameters <- get_region_sinusoids(c("Hawaii", "Alaska"))[[2]]
order <- region_sinusoids_parameters |> arrange(-Phase) |> pull(Region)
order_df <- data.frame(Region = str_to_title(order), num = c(1:4))
regions_colors <- left_join(colors_df, order_df) |> arrange(num)
region_sinusoids_parameters <- region_sinusoids_parameters |> mutate(Region = factor(Region, order))
region_phase_plot <- region_sinusoids_parameters |> 
  mutate(lower = Phase - 1.96*Phase_SE, upper = Phase + 1.96*Phase_SE) |>
  ggplot(aes(x = Phase %% 12, y = Region, color = Region)) + geom_point() + geom_errorbar(aes(xmin = lower %%12, xmax = upper %%12), width = 0.2) + 
  theme_minimal() + 
  # ggtitle(paste("Phase Estimates for Region Sinusoids")) + 
  ylab("Region") + xlab("Month")+
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  scale_color_manual(values= regions_colors$region_color, labels=regions_colors$Region) +
  scale_y_discrete(labels=levels(region_sinusoids_parameters$Region))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size = 20))
```


Fit sinusoids to subregional data and plot. Becomes Supplementary Figure 8a.
```{r supplementary figure 7a}
subregion_sinusoids <- get_subregion_sinusoids(c("Hawaii", "Alaska"))[[1]] |>
  mutate(Region = factor(part, c("East South Central", "West South Central",
                                      "West North Central", "South Atlantic", "Middle Atlantic",
                                      "Mountain West", "East North Central", "New England", "Pacific West")))
subregion_sinusoids_CIs_plot_points <- subregion_sinusoids |>
  ggplot(aes(x=MONTH)) + 
  geom_line(aes(x= MONTH, y = prediction, color = Region), linetype = 2) + 
  geom_point(aes(x= MONTH, y = yearly_average_sum_region_cases_per_thousand, color = Region), size = 1, data = subregion_sinusoids) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill= Region), alpha = 0.2) +
  # ggtitle("Streptococcal Pharyngitis Visits Subregion Sinusoidal Fits") +
  labs(color = "Subregion", fill = "Subregion") + 
  ylab("Visits per 1,000 People") +
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  scale_color_manual(values= subcolors_df$region_color, labels=subcolors_df$Region) +
  scale_fill_manual(values= subcolors_df$region_color, labels=subcolors_df$Region) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size = 20))
```

Plot subregion phases. Becomes Supplementary Figure 8b.
```{r subregion phases, supplementary figure 7b}
subregion_sinusoids_parameters <- get_subregion_sinusoids(c("Hawaii", "Alaska"))[[2]]
order <- subregion_sinusoids_parameters |> arrange(-Phase) |> pull(Region)
order_df <- data.frame(Region = order, num = 1:9)
subregions_colors <- left_join(subcolors_df, order_df) |> arrange(num)
subregion_sinusoids_parameters <- subregion_sinusoids_parameters |> mutate(Region = factor(Region, order))
subregion_phase_plot <- subregion_sinusoids_parameters |> 
  mutate(lower = Phase - 1.96*Phase_SE, upper = Phase + 1.96*Phase_SE) |>
  ggplot(aes(x = Phase %% 12, y = Region, color = Region)) + geom_point() + geom_errorbar(aes(xmin = lower %%12, xmax = upper %%12), width = 0.2) + 
  theme_minimal() +
  # ggtitle(paste("Phase Estimates for Subregion Sinusoids")) +
  ylab("Subregion") + xlab("Month")+
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  scale_color_manual(name = "Subregion", values= subregions_colors$region_color, labels=gsub("_", " ",subregions_colors$Region , fixed=TRUE)) +
  scale_y_discrete(labels=levels(subregion_sinusoids_parameters$Region)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size = 20)) 
```

Save region and subregion sinusoid phases into tables
```{r save parameters}

#Calculate subregion phases and 95% CIs
subregion_sinusoids_phase_table <- subregion_sinusoids_parameters |> 
  arrange(Phase) |>
  mutate(lower = Phase - 1.96*Phase_SE, upper = Phase + 1.96*Phase_SE) |>
  mutate(CI = paste0("(", round(lower,2),"-", round(upper,2), ")")) |>
  mutate(Phase_CI = paste(round(Phase, 2), CI)) |>
  mutate(Subregion = Region) |>
  select(Subregion, Phase_CI)

#Calculate region phases and 95% CIs
region_sinusoids_phase_table <- region_sinusoids_parameters |> 
  arrange(Phase) |>
  mutate(lower = Phase - 1.96*Phase_SE, upper = Phase + 1.96*Phase_SE) |>
  mutate(CI = paste0("(", round(lower,2),"-", round(upper,2), ")")) |>
  mutate(Phase_CI = paste(round(Phase, 2), CI)) |>
  mutate(Subregion = Region) |>
  select(Subregion, Phase_CI)

```



Calculate subregion centroids. Becomes Supplementary Figure 7a. 
```{r centroid analysis figure S7}
#load state centroid data from 2010 from USpopcenters package
state_centroid <- state2010 |>
  mutate(id = STNAME, lat = LATITUDE, long = LONGITUDE) |> 
  select(STATEFP, POPULATION, lat, long, id) |>
  filter(!id %in% c("Hawaii", "Alaska", "Puerto Rico"))

#change Washington DC to District of Columbia for mapping purposes
subregions_centroid <- subregions
subregions_centroid[which(subregions_centroid$STATE == "Washington DC"),1] = "District of Columbia"

#adjust state centroid format for joining
state_centroid_subregions <- state_centroid |> 
  mutate(STATE = id) |> 
  select(-id) |> 
  left_join(subregions_centroid)

#calculate the total populations in each subregion 
total_pops <- state_centroid_subregions |> 
  group_by(part) |>
  summarize(total_pop = sum(POPULATION))
sum(total_pops$total_pop) #sum is ~307,000,000 which makes sense for 2010 minus Hawaii/Alaska

#calculate population weighted average of state centroids
subregion_centroids <- state_centroid_subregions |> 
  left_join(total_pops) |> 
  mutate(state_weight = POPULATION/total_pop) |>
  mutate(weighted_lat = lat*state_weight,
         weighted_long = long*state_weight) |>
  group_by(part) |>
  summarize(subregion_lat = sum(weighted_lat), subregion_long = sum(weighted_long))
continental_fortified_tojoin_subregions <- continental_fortified_tojoin |> 
  mutate(STATE = id) |> left_join(subregions_centroid) |> 
  mutate(Region = factor(part, levels = c("East South Central", "West South Central",
                                          "West North Central", "South Atlantic", "Middle Atlantic",
                                          "Mountain West", "East North Central", "New England", "Pacific West")))

#calculate a distance reference point as the average between the two South regions with the earliest starts
ref_point <- subregion_centroids |> 
  filter(part %in% c("West South Central", "East South Central")) |> 
  left_join(total_pops) |>
  mutate(weight = total_pop / sum(total_pop)) |>
  mutate(weighted_lat = subregion_lat*weight,
         weighted_long = subregion_long*weight) |>
  summarize(ref_lat = sum(weighted_lat), ref_long = sum(weighted_long))

#plot subregions with their centroids and the reference point 
subregion_centroids_plot <- ggplot() + 
  geom_polygon(data = continental_fortified_tojoin_subregions, aes(x = long, y = lat, group = group, fill = Region), color="black", alpha = 0.5) +
  scale_fill_manual(name = "Subregion", values = subcolors_df$region_color, labels = subcolors_df$Region) +
  geom_point(data =subregion_centroids, aes(x = subregion_long, y = subregion_lat), color = "black", size = 3) +
  geom_point(data = ref_point, aes(x = ref_long, y = ref_lat), color = "red", size = 5) +
  theme_void() + ggtitle("") + 
  theme(plot.title = element_text(hjust = 0.5, size = 25),
        plot.subtitle = element_text(hjust = 0.5, size = 23),
        legend.position = 'bottom') 

```

Calculate distances from each subregion to the centroid and correlate with phases. Becomes Supplementary Figure 7b. 
```{r centroid analysis figure S7b}
#calculate euclidean distance and store in dataframe
dist_df <- data.frame(Subregion = subregion_centroids$part, 
                      dist = NA)
for(i in 1:length(dist_df$Subregion)){
  point <- subregion_centroids |> filter(part == dist_df$Subregion[i]) 
  dist_df$dist[i] = sqrt((point$subregion_lat - ref_point$ref_lat)^2 + (point$subregion_long - ref_point$ref_long)^2)
}

#find subregion phases
subregion_phase <- subregion_sinusoids_parameters |> 
  mutate(Subregion = factor(Region, levels = c("East South Central", "West South Central",
                                          "West North Central", "South Atlantic", "Middle Atlantic",
                                          "Mountain West", "East North Central", "New England", "Pacific West"))) |>
  select(Subregion, Phase) |> arrange(Subregion)
dist_df <- dist_df |> mutate(Subregion = factor(Subregion, levels = subregion_phase$Subregion)) |>
  arrange(Subregion)

cor(dist_df$dist, subregion_phase$Phase) #correlation is 0.7276

subregion_phase_dist_correlation <- left_join(subregion_phase, dist_df) |> 
  mutate(Region = Subregion) |> 
  left_join(subcolors_df) |> ggplot(aes(x = Phase, y = dist)) +
  geom_point(aes(color = Subregion)) + 
  theme_minimal() + geom_smooth(method = 'lm', color = 'black', linewidth = 0.3,linetype = 2, alpha = 0.2) +
  scale_color_manual(values = subcolors_df$region_color, labels = subcolors_df$Region) +
  ylab("Distance")

subregion_phase_dist_correlation_forfig <- subregion_phase_dist_correlation + theme(legend.position = "none")

```

Load in trimmed school start data, calculate uptick points and plot. Becomes Supplementary Figure 11.
```{r school start date,figS11}
#summarize school start data
start_date_summary <- read_csv("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/school_starts_summary.csv")

subcolors_df_ordering <- data.frame(Subregion = c("East South Central", "West South Central",
                                      "West North Central", "South Atlantic", "Middle Atlantic",
                                      "Mountain West", "East North Central", "New England", "Pacific West"),
                           region_color = c(pal[6], pal[5], pal[4], pal[9], pal[2], pal[8], pal[3], pal[1], pal[7])) |> mutate(Subregion = factor(Subregion, levels = c("West South Central", "East South Central", "Mountain West",
                                                                                                               "West North Central", "South Atlantic", "East North Central", 
                                                                                                               "Pacific West", "Middle Atlantic", "New England"))) |> arrange(Subregion)


#calculate uptick points
region_totals <- pop_sizes |> 
  filter(!STATE %in% c("Hawaii", "Alaska")) |>
  left_join(subregions) |>
  group_by(part) |>
  summarize(region_total = sum(POPSIZE))

subregion_weightedvis_allyears <- left_join(dat, coh) |> left_join(subregions) |> left_join(pop_sizes) |>
  filter(!STATE %in% c("Hawaii", "Alaska")) |>
  left_join(region_totals) |>
  mutate(pop_frac = POPSIZE / region_total) |>
  mutate(group_weight = pop_frac/NMEMB) |>
  mutate(weighted_vis = NVISITS*group_weight) |>
  group_by(part, YEAR, MONTH) |>
  summarize(sum_region_vis_perthous = sum(weighted_vis)*1000)

#make a dataframe to fill that just has the regions and the years and a place to put the min month
month_mins <- expand_grid(YEAR = c(2010:2018), part = c("East South Central", "West South Central",
                                                        "West North Central", "South Atlantic", "Middle Atlantic",
                                                        "Mountain West", "East North Central", "New England", "Pacific West"), min = NA)

#fill dataframe
for(i in 1:nrow(month_mins)){
  df <- subregion_weightedvis_allyears |>
    filter(YEAR == month_mins[i,1], part == month_mins[i,2])
  month_mins[i,3] <- df[which(df$sum_region_vis_perthous == min(df$sum_region_vis_perthous)), 3]
}
#summarize month mins to have an average minimum month across all years for each region
avg_month_mins <- month_mins |> group_by(part) |> summarize(mean_min = mean(min), sd = sd(min)) |> mutate(lower = mean_min - 1.96*sd/3, upper = mean_min + 1.96*sd/3) |>
  mutate(Subregion = factor(part, levels = c("West South Central", "East South Central", "Mountain West",
                                                                                                               "West North Central", "South Atlantic", "East North Central", 
                                                                                                               "Pacific West", "Middle Atlantic", "New England"))) |>
  arrange(Subregion)

#arrange data for plotting
avg_subregionvis <- subregion_weightedvis_allyears |>
  group_by(part, MONTH) |> 
  summarize(avg_vis_perthous = mean(sum_region_vis_perthous), sd_vis = sd(sum_region_vis_perthous)) |>
  left_join(avg_month_mins) |> 
  mutate(lower = avg_vis_perthous - 1.96*sd_vis / 3, upper = avg_vis_perthous + 1.96*sd_vis / 3) |> 
  mutate(Region = Subregion) |>
  left_join(subcolors_df) |> arrange(Subregion)

subregion_uptick_plot <- avg_subregionvis |> 
  ggplot(aes(x = MONTH, y = avg_vis_perthous)) + geom_line(aes(color = Subregion)) +
  geom_ribbon(aes(x = MONTH, ymin = lower, ymax = upper, fill = Subregion), alpha = 0.2) + 
  theme_minimal() + scale_color_manual(values = subcolors_df_ordering$region_color) + geom_vline(aes(xintercept = mean_min), color = 'black', linetype = 2, alpha = 0.5) +
  scale_fill_manual(values = subcolors_df_ordering$region_color) + 
  facet_wrap(~Subregion) +
  ylab("Average Visits per 1000") +
  xlab("Month") +
  scale_x_discrete(limits = c("JAN", "FEB", "MAR", "APR", "MAY", "JUN", "JUL", "AUG", "SEPT","OCT", "NOV", "DEC")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


avg_month_mins |> mutate(Date = date(duration(month = mean_min-1)), lower_date = date(duration(month = lower-1)),
                         upper_date =date(duration(month = upper-1)), cat = "Min Visit Date")
min_uptick_order <- avg_month_mins |> arrange(mean_min) |> pull(part)

month_mins_date <- avg_month_mins |> mutate(Date = date(duration(month = mean_min-1))-1, lower_date = date(duration(month = lower-1))-1,
                         upper_date =date(duration(month = upper-1))-1, cat = "Min Visit Date") |> 
  select(Subregion, Date, lower_date, upper_date, cat)

year(month_mins_date$Date) <- 2019
year(month_mins_date$lower_date) <- 2019
year(month_mins_date$upper_date) <- 2019

#combine school start and month min data into 1 dataframe for plotting
comb <- rbind(start_date_summary, month_mins_date) |> mutate(Subregion = factor(Subregion, levels = rev(min_uptick_order)))
uptickdates_plot <- comb |> ggplot(aes(x = Date, y = Subregion, color = cat)) + geom_point() + geom_errorbar(aes(xmin = lower_date, xmax = upper_date), width = 0.2, alpha = 0.5) +
  theme_minimal() + labs(color = "Date")



```

Correlate start dates with uptick dates. Becomes Figure 3. 
```{r, correlation fig 3}
start_date <- start_date_summary |> mutate(reg = factor(Subregion, levels = rev(min_uptick_order))) |> arrange(reg) |> mutate(DateSS = Date) |> select(reg, DateSS)
min_date <- month_mins_date |> mutate(reg = factor(Subregion, levels = rev(min_uptick_order))) |> arrange(reg) |>
  mutate(DateMin = Date) |> select(reg, DateMin)
date_summaries <- left_join(start_date, min_date) |> mutate(dif = DateSS-DateMin)
range(date_summaries$dif) #28 to 47 days
min(date_summaries$dif) #28 days
max(date_summaries$dif) #47 days
mean(date_summaries$dif) #36.2 days

df_toplot <- left_join(comb, subcolors_df_ordering) |> pivot_wider(names_from = cat, values_from = c(Date, lower_date, upper_date)) |>
  mutate(Subregion = factor(Subregion, levels = min_uptick_order)) |> arrange(Subregion)

corrplot_schoolstart <- df_toplot |>
  ggplot(aes(x = Date_SchoolStart, y = `Date_Min Visit Date`)) + geom_point(aes(color = Subregion)) + scale_color_manual(values = df_toplot$region_color) +
  theme_minimal() + geom_smooth(method = 'lm', color = 'black', linewidth = 0.3,linetype = 2, alpha = 0.2) + 
  xlab("Average School Start Date") + ylab("Minimum Visit Date") 

```
Bootstrap correlation 
```{r school start correlation bootstrapping}
#bootstrap the uptick dates by sampling one of the 9 min dates from each subregion
subregions_vec <- c("West South Central", "East South Central", "Mountain West",
                "West North Central", "South Atlantic", "East North Central", 
                "Pacific West", "Middle Atlantic", "New England")
booted_min <- data.frame(samp = 1:1000)
for(i in 1:9){
  tmp <- month_mins |> filter(part == subregions_vec[i]) |> pull(min)
  booted_min <- cbind(booted_min, tmp = sample(tmp, 1000, replace = TRUE))
}
colnames(booted_min) <- c("samp", subregions_vec)
booted_school <- readRDS("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/booted_school.RDS")



#make a vector to calculate the correlations between all 1000 pairs of vectors
vec <- c()
for(i in 1:1000){
  tmp <- cor(c(t(booted_min[i,]))[2:10],c(t(as.numeric(booted_school[i,])))[2:10])
  vec <- append(vec, tmp)
}

quantile(vec, probs = c(0.025, 0.5, 0.975))

#2.5%         50%       97.5% 
# -0.04099167  0.52706967  0.91195631 

```


```{r}
#write all tables
write_csv(table1, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/study_population_table_table1.csv")
write_csv(region_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/Average_region_year.csv")
write_csv(subregion_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/Average_subregion_year.csv")
write_csv(region_table_month, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/Average_region_month.csv")
write_csv(subregion_table_month, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/Average_subregion_month.csv")
write_csv(region_quarters_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/region_quarters_table.csv")
write_csv(subregion_quarters_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/subregion_quarters_table.csv")
write_csv(quarter_diffs_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/quarter_diffs_region_table_S4.csv")
write_csv(wide_table_regions, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/continental_US_regions_table_wide.csv")
write_csv(wide_table_subregions, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/continental_US_subregions_table_wide.csv")
write_csv(phase_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/State_phase_table_S5.csv")
write_csv(subregion_sinusoids_parameters, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/subregion_sinusoids_parameters.csv")
write_csv(region_sinusoids_parameters, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/region_sinusoids_parameters.csv")
write_csv(subregion_sinusoids_phase_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/subregion_phase_table.csv")
write_csv(region_sinusoids_phase_table, "/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/output/region_phase_table.csv")

#save all figures as pngs and pdfs
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS1.png", continental_state_membership_noSC, width = 10, height = 5)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS1.pdf", continental_state_membership_noSC, width = 10, height = 5)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2a.png", region_differences_byyear, width = 10, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2a.pdf", region_differences_byyear, width = 10, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2b.png", year_averages_plot, width = 10, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2b.pdf", year_averages_plot, width = 10, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2c.png", region_comparisons, width = 10, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2c.pdf", region_comparisons, width = 10, height = 7)

#put multi-panel figures together
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2.pdf", grid.arrange(region_differences_byyear_forfig, year_averages_plot, region_comparisons, layout_matrix = rbind(c(1,1,2,2), c(4,3,3,4))), width = 12, height = 10)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS2.png", grid.arrange(region_differences_byyear_forfig, year_averages_plot, region_comparisons, layout_matrix = rbind(c(1,1,2,2), c(4,3,3,4))), width = 12, height = 10)

ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3a.png", subregion_differences_byyear, width = 10)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3a.pdf", subregion_differences_byyear, width = 10)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3b.png", year_averages_plot_subregions)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3b.pdf", year_averages_plot_subregions)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3c.png", subregion_comparisons, width = 12, height = 9)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3c.pdf", subregion_comparisons, width = 12, height = 9)

ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3.pdf", grid.arrange(subregion_differences_byyear_forfig, year_averages_plot_subregions, subregion_comparisons, layout_matrix = rbind(c(1,1,1,2,2,2),c(1,1,1,2,2,2), c(4,3,3,3,3,4),c(4,3,3,3,3,4), c(4,3,3,3,3,4))), width = 12, height = 10)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS3.png", grid.arrange(subregion_differences_byyear_forfig, year_averages_plot_subregions, subregion_comparisons, layout_matrix = rbind(c(1,1,1,2,2,2),c(1,1,1,2,2,2), c(4,3,3,3,3,4),c(4,3,3,3,3,4), c(4,3,3,3,3,4))), width = 12, height = 10)

ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/fig1.png", points_region_plot, width = 9, height =7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/fig1.pdf", points_region_plot, width = 9, height =7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS4.png", points_subregion_plot, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS4.pdf", points_subregion_plot, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS5a.png", region_quarters_plot, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS5a.pdf", region_quarters_plot, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS5b.png", subregion_quarters_plot, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS5b.pdf", subregion_quarters_plot, width = 9, height = 7)

#layout quarters plot for figure
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS5.pdf", grid.arrange(region_quarters_plot, subregion_quarters_plot), width = 9, height = 14)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS5.png", grid.arrange(region_quarters_plot, subregion_quarters_plot), width = 9, height = 14)


ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS6a.png", region_heatmap_significance_noredund, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS6a.pdf", region_heatmap_significance_noredund, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS6b.png", subregion_heatmap_significance_noredund, width = 9, height = 9)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS6b.pdf", subregion_heatmap_significance_noredund, width = 9, height = 9)
#layout heatmaps for figure
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS6.pdf", grid.arrange(region_heatmap_significance_noredund, subregion_heatmap_significance_noredund), width = 9, height = 16)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS6.png", grid.arrange(region_heatmap_significance_noredund, subregion_heatmap_significance_noredund), width = 9, height = 16)

ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/fig2.png", state_phases_map_noSC, width = 9, height = 6.5)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/fig2.pdf", state_phases_map_noSC, width = 9, height = 6.5)

#save fig S7 individual components
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS7a.png", subregion_centroids_plot, width = 9, height = 6.5)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS7a.pdf", subregion_centroids_plot, width = 9, height = 6.5)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS7b.png", subregion_phase_dist_correlation, width = 9, height = 6.5)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS7b.pdf", subregion_phase_dist_correlation, width = 9, height = 6.5)
#save fig S7 layout
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS7.png", grid.arrange(subregion_centroids_plot, subregion_phase_dist_correlation_forfig, ncol = 1), width = 9, height = 13)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS7.pdf", grid.arrange(subregion_centroids_plot, subregion_phase_dist_correlation_forfig, ncol = 1), width = 9, height = 13)


ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS8a.png", subregion_sinusoids_CIs_plot_points, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS8a.pdf", subregion_sinusoids_CIs_plot_points, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS8b.png",subregion_phase_plot, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS8b.pdf",subregion_phase_plot, width = 9, height = 7)

#layout sinusoid plots and phases
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS8.pdf", grid.arrange(subregion_sinusoids_CIs_plot_points, subregion_phase_plot), width = 9, height = 14)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS8.png", grid.arrange(subregion_sinusoids_CIs_plot_points, subregion_phase_plot), width = 9, height = 14)

ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS9a.png", region_sinusoids_CIs_plot_points, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS9a.pdf", region_sinusoids_CIs_plot_points, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS9b.png", region_phase_plot, width = 9, height = 7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS9b.pdf", region_phase_plot, width = 9, height = 7)

#layout region sinusoids
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS9.pdf", grid.arrange(region_sinusoids_CIs_plot_points, region_phase_plot), width = 9, height = 14)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS9.png", grid.arrange(region_sinusoids_CIs_plot_points, region_phase_plot), width = 9, height = 14)


ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS10.png", state_sinusoids_subregions, width =10, height =7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS10.pdf", state_sinusoids_subregions, width =10, height =7)

ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS11a.png", subregion_uptick_plot, width =10, height =7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS11a.pdf", subregion_uptick_plot, width =10, height =7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS11b.png", uptickdates_plot, width =10, height =7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS11b.pdf", uptickdates_plot, width =10, height =7)

#layout figure S11
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS11.png", grid.arrange(subregion_uptick_plot, uptickdates_plot), width =10, height =14)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/figS11.pdf", grid.arrange(subregion_uptick_plot, uptickdates_plot), width =10, height =14)


ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/fig3.png", corrplot_schoolstart, width =10, height =7)
ggsave("/Users/madeleinekline/Dropbox (Harvard University)/G1/GradLab/StrepPharyngitis/figures/fig3.pdf", corrplot_schoolstart, width =10, height =7)



```

make gif, this step takes a while
```{r}
source('make_gif.R')
```

